Something that is not PCADSC

### 2017-01-25 article/article_v0.01.tex
Update article_v0.01.tex

\section{Introduction}
\label{sec:introduction}
The origin stories of datasets have largely changed over time. While data was often gathered with a specific scientific inquiry in mind in the past, a lot of data is accumulated without such a specific purpose nowadays. This is both due to the vast amounts of data registrations online and due to a trend towards more open source research in a lot of different scientific disciplines. Especially the latter phenomenon poses new challenges with respect to data quality assessment. When data is collected and made public without a specific end-point in mind, how do we ensure that e.g. differences in measurement instruments do not cause the data to be effectively divided into subsets that are simply not comparable?

A lot of sophisticated methods are available for answering this type of question when we are willing to assume a statistical model of some sort. But when these models are taken away, a remarkable void of methods is left behind. What is needed is a procedure that compares differences in overall data structures in two (or more) subsets of a dataset without assuming neither directional nor hierarchical relationships between the variables. We propose a new method for this task, namely Principal Component Analysis-based Data Structure Comparison (PCADSC). This method employs the principal component decomposition of the data matrix performed on two subsets of a dataset in order to create intuitive visualizations of data structure differences. \hl{Mention R package.}

>>>>

\section{Introduction}
\label{sec:introduction}
The origin stories of datasets have changed over time. While data, in the past, data was collected with a specific scientific inquiry in mind, today, a lot of data is accumulated without a specific purpose. This is due to vast amounts of data being registered online and due to a trend towards more open source research. The latter phenomenon, in particular poses new challenges wrt.\ data quality assessment. When data are collected and made public without a specific end-point in mind, how do we ensure that e.g.\ differences in measurement instruments do not cause the data to be effectively divided into subsets that are simply not comparable?

Sophisticated methods for addressing this question are available when we are willing to assume a statistical model, but when these models are taken away, a remarkable void of methods is left behind. What is needed is a procedure that compares differences in overall data structures in two (or more) subsets of a dataset without assuming neither directional nor hierarchical relationships between the variables. We propose a new method for this task, namely Principal Component Analysis-based Data Structure Comparison (PCADSC). This method employs the principal component decomposition of the data matrix performed on two subsets of a dataset in order to create intuitive visualizations of data structure differences. \hl{Mention R package.}
